First, I want to thank my primary supervisor, Christian Gehrmann. During my work, he has always supported me, given me invaluable feedback, and guided me in my work. My other supervisor, Martin Hell, also deserves a big thanks for his valuable input and guidance during my work.

A special thanks have to go to Ludwig Seitz. He can take credit for leading me onto the research path. He also has been a good and thoughtful supervisor and always a great company.

I also want to thank the rest of the Ph.D. students and Seniors in the Crypto and Security group.
You have all helped to create an excellent research environment and a fun place to work.

Thanks also to my colleagues at RISE. To the Cybersecurity Lab, I want to thank you for fruitful collaborations and an inspiring research climate. I want to give a special thanks to Simon, for his invaluable help with Tamarin Prover and to Marco and Richard for their willingness to help and guide me with the intricacies of OSCORE.

To my RISE colleagues in Lund, a special thanks go to Arash and Thomas. Thank you for your patience and support during my time at SICS and then RISE.

Last but not least, I want to thank my family and friends. Thank you for your support and understanding during long nights and weekends of work.
To my dear family: mom Karin, dad Svante, and siblings Maria and Olof. Thank you so much for your unyielding support and encouragement. I doubt I would have been able to finish this thesis without you.

% Signature.
\begin{flushright}
	\emph{Martin}
	
	Lund, March 2020
\end{flushright}